Results

### 2019-05-03 analysis/survey/preregistration.Rmd
Add reserach questions

ANDREW TODO: Finish this section

@@

1. Donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming. Previous research has found that structural characterists are common heuristics for donors. Organizational vs. structural heuristics

2. How those interact with individual characteristics

3. What is the optimal mix of attribute levels?

We are interested in whether the contentiousness of an NGO’s relationship with its host government influences donor decision making. Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?

We are also interested in the effect of organizational characteristics on donor decision making. Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?

To test possible confounding and mediating effects, we also plan to see how donor characteristics influence the decision to donate, including political ideology, political knowledge, religious attendance, involvement in charitable activities, involvement in activism, and other demographic characteristics.

>>>>

@@

1. **Do donors rely on structural characteristics of NGOs as heuristics when deciding to donate? How do structural heuristics compare to organizational heuristics?**

	Donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming. Previous research has found that an NGO's organizational characteristics commonly serve as heuristics for donors. Donors use an organization's overhead costs, the issues it works on, its transparency and accountability practices, and a host of other organizational practices as signals of an organization's efficiency and deservingness, which then influences their decision to make a donation. These kinds of heuristics are attributes that organizations can typically control—NGOs can publish annual reports, restructure their management, and engage in other strategies to appear more worthy of donation.

	Structural characteristics, such as the political and legal environment an NGO faces in its host country, may also serve as signals to donors of NGO deservingness. We are interested in whether the contentiousness of an NGO’s relationship with its host government influences donor decision making. Do donors care if nonprofits they care about are criticized by, persecuted by, or expelled from the countries they work in?

	We are also interested in the effect of organizational characteristics on donor decision making. How do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) compare to structural characteristics when deciding to donate? Which heuristics are more influential?

2. **How do individual-level donor characteristics interact with structural and organizational heuristics? Which kinds of people are more or less likely to consider an NGO's host country political environment, managerial practices, funding sources, or issue area?**

	The decision to donate to an NGO is not determined solely by an organization's characteristics. Donors themselves have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy. We are interested in how individual donor characteristics, such as political ideology, political knowledge, religious attendance, involvement in charitable activities, involvement in activism, and demographic attributes interact with organizational- and structural-level factors.

3. **What is the optimal mix of attribute levels for NGOs interested in maximizing donations?**

	Finally, given individual donor characteristics and preferences, we are interested in finding the optimal mix of organizational and structural attributes. What might an NGO try to emphasize in its marketing campaigns? Should it highlight its funding sources, managerial practices, issue area, or relationship with its host governments (even if that relationship is negative)?
